\documentclass[11pt,a4paper]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{currvita}
\usepackage{xcolor}
\usepackage{hyperref}

\hypersetup{%
  colorlinks=false,
  urlbordercolor=red
}

\titleformat{\section}{\scshape\large}{}{0em}{}[\titlerule]
%\titleformat{\subsection}{\bfseries\raggedright\large}{}{0em}{}




\begin{document}

\date{}
\thispagestyle{empty}
\setlength\cvlabelwidth{90pt}

\begin{cv}{\huge Curriculum Vitae of Massimiliano Furlan \large{[\today ]}}

\section{Contacts}

\begin{cvlist}{}
	\itemsep -4pt
	\item[Email:] \href{mailto:massimiliano.furlan[at]studio.unibo.it}{massimiliano.furlan[at]studio.unibo.it}
	\item[Website:] \href{https://massimilianofurlangit.github.io}{massimilianofurlangit.github.io}
\end{cvlist}
\vspace{-20pt}

\section{Personal Information}

\begin{cvlist}{}
	\itemsep -4pt
	\item[Birth date:] 23 November 1995
	\item[Nationality:] Italian
\end{cvlist}
\vspace{-20pt}

\section{Education}

\begin{cvlist}{}
	\item[starting 09/2022] 
		\textbf{MRes., Economics}\\ 
		University of Warwick, Coventry, United Kingdom
		%\textbf{Thesis:} \href{https://www.teses.usp.br/teses/}{Extremely long title of my thesis}\\
		%\textbf{Advisor:} {xxxxxx xxxxxx}\\
		%\textbf{Co-Advisor:} {xxxxxx xxxxxx xxxxxx}
	\item[09/2020 -- 07/2022] 
		\textbf{Master's Degree, Economics}\\ 
		 Mater Studiorum -- University of Bologna, Bologna, Italy\\
		Thesis: Algorithmic pricing with coarse memory\\
		Advisor: Vincenzo Denicolò\\
		Final grade: 110/110 \hspace{38pt} (GPA: 29.5/30)
	\item[09/2017 -- 10/2020] 
		\textbf{Bachelor's Degree, Economics and Business}\\
		Ca' Foscari University of Venice, Venice, Italy\\
		Thesis: Cognitive limits in team theory\\
		Advisor: Marco LiCalzi\\
		Final grade: 110 cum laude \quad (GPA: 27.9/30)	
\end{cvlist}
\vspace{-20pt}

\section{Academic Experience}

\begin{cvlist}{}
	\item[08/2021 -- 09/2021]
		\textbf{Alma Mater Studiorum – University of Bologna}\\
		Position: Research assistant\\
		Supervisor: Vincenzo Denicolò\\
		Project: Artificial Intelligence, Algorithmic Pricing and Collusion\\
		Activities: Replication of \href{https://www.aeaweb.org/articles?id=10.1257/aer.20190623}{Calvano et al. (2020)} in JuliaLang.
\end{cvlist}
\vspace{-20pt}

\section{Volunteering}
\begin{cvlist}{}
	\item[05/2021 -- 07/2021]
		\textbf{Alma Mater Studiorum – University of Bologna}\\
		Position: Mentor -- Orienta|ME project\\
		Activities: Gave support to two high school students during their decision-making process for university choice in a field of study in economics.
\end{cvlist}
\vspace{-20pt}

%\section{Honors, Awards \& Scholarships}
\section{Grants and Scholarships}
\begin{cvlist}{}
	\itemsep -4pt
	\item[2022] Departmental Scholarship, Department of Economics, University of Warwick 
	\item[2020] Study Grant, Department of Economics, University of Bologna
\end{cvlist}


%   \vspace{-1cm}
\section{Additional Skills}
\begin{cvlist}{}
	\item[Languages:] 
		Italian: native \ | \
		English: TOEFL 113/120
	\item[IT Skills] 
		I primarily use macOS, but I also use Linux (Debian). During high school, I studied C, Java and SQL. In the last year I used Stata, MATLAB, R and Python. Currently, I’m using Julia for my thesis work. I typeset in LATEX.
\end{cvlist}


\end{cv}

\end{document}
\endinput
%%
%% End of file `cvtest.tex'.
